Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors That Have Mixed During Cooling

### 2019-09-23 paper/reply_to_referee.txt

> - It is not clear to me if the input deflagration speed (pg 7) has been
> recalibrated to the particular initial composition of the mixed hybrid
> core. Willcox et al (2016) just reports recomputing detonations, but there
> is no mention of deflagrations (at least I have not been able to find it).

We regret no explaining the methodology of our deflagration speeds. The 
answer is that the deflagration speeds for input to the flame model are 
from tabulated results. Laminar flame speeds are first 
obtained by interpolation within a
three-dimensional table of 12C, 22Ne, and log density obtained from
prior direct numerical simulations. Here 22Ne is uses as a proxy for
for neutron-rich elements so the interpolated laminar flame speeds capture
the boost due to neutronization. These laminar flame speed are
then boosted to account for the effects of unresolved buoyancy
and background turbulence and passed to the flame model. We have
updated the text of the manuscript to explain the flame speeds
and included a citation to earlier work describing the tabulated
flame speeds in detail.

[AC NOTE: CHECK THE ABOVE. The models include 20Ne. Does the above
description properly account for that? As I recall, nothing new
was done to the tables for the hybrid Willcox et al. models.]

[rephrasing the question- does 20Ne count as fuel for both
the energy release and the flame speed from the table? Don seems 
to recall that we had the energy release of burning 20Ne in the 
detonation tests, which says it was included for the energy 
release. But do we just consider 12C + 12C buring for the
flame speed?]

Also, the detonation tests in Willcox et al. were tests of the
energy release of the flame model and not flame speed tests. The 
model releases identical amounts of energy for both deflagrations and 
detonations in identical material, so detonation simulations were
a simple check of the modifications we made to the model to
include 20Ne in the mix.

### 2019-10-03 paper/ms.tex
fix typo.

The single degenerate picture posits a white dwarf gaining mass
from a companion, and the process relies on a long
period of accretion combined with either steady burning or a
series of nova explosions for a traditional
C-O WD to gain the $\sim 0.4$ \Msun\ needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As the WD approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear burning that will incinerate the star.
Within this progenitor setting, models that best reproduce observations 
are those in which the burning begins as a subsonic deflagration
during which the star expands that is then followed by supersonic 
detonation~\citep{Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05,
hillebrandtetal2013,calderetal2013}. We simulate thermonuclear explosion 
properties assuming this scenario and our describe  methodology in 
detail below.

The double detonation picture also has a white dwarf gaining mass from 
a companion. The supernova begins with 
a detonation occurring in an accreted layer of He, and that subsequently triggers 
another detonation in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
nomoto80,nomoto82b}. Early studies indicated that this scenario could work 
for a wide range of white dwarf masses, not just the near-Chandrasekhar case 
\citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
scenario \citep{ww94}. The mass of accretted He 
is a concern because heavier
elements synthesized in the He detonation will appear in
the outer ejecta, which does not match observations~\citep{HoefKhok96,
hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
however, found that fairly thin He layers could flash on sub-Chandrasekhar
mass white dwarfs, encouraging
further research~\citep{simetal2012,brooksetal2015,shenetal2018,
glasneretal2018,Townsleyetal2019}.

>>>>

The single degenerate picture posits a white dwarf gaining mass
from a companion, and the process relies on a long
period of accretion combined with either steady burning or a
series of nova explosions for a traditional
C-O WD to gain the $\sim 0.4$ \Msun\ needed for it to approach the
limiting Chandrasekhar mass~\citep{starrfieldetal2012}. As the WD approaches
the Chandrasekhar limit, conditions in the compressed core are right
to ignite the thermonuclear burning that will incinerate the star.
Within this progenitor setting, models that best reproduce observations 
are those in which the burning begins as a subsonic deflagration
during which the star expands that is then followed by supersonic 
detonation~\citep{Khokhlov1991Delayed-detonat,HoefKhok96,GameKhokOran05,
hillebrandtetal2013,calderetal2013}. We simulate thermonuclear explosion 
properties assuming this scenario and describe our methodology in
detail below.

The double detonation picture also has a white dwarf gaining mass from 
a companion. The supernova begins with 
a detonation occurring in an accreted layer of He, and that subsequently triggers 
another detonation in the underlying white dwarf \citep{woosleyweavertaam80,taam80a,taam80b,
nomoto80,nomoto82b}. Early studies indicated that this scenario could work 
for a wide range of white dwarf masses, not just the near-Chandrasekhar case 
\citep{livne90}, hence the moniker ``sub-Chandrasekhar'' also applied to this 
scenario \citep{ww94}. The mass of accreted He
is a concern because heavier
elements synthesized in the He detonation will appear in
the outer ejecta, which does not match observations~\citep{HoefKhok96,
hoeflichetal96,finkhillebrandtroepke2007,simetal2010}.  \citet{bildstenetal2007},
however, found that fairly thin He layers could flash on sub-Chandrasekhar
mass white dwarfs, encouraging
further research~\citep{simetal2012,brooksetal2015,shenetal2018,
glasneretal2018,Townsleyetal2019}.
